How to Analyze Build Logs---A~Comparative Study of Chunk~Retrieval~Techniques

### 2020-04-07 tse-paper/content.tex
Align lit survey figure with text

% TODO (Caro): Integrate Petersen's guidelines
From our own experience, we know that the field of analyzing build
logs is relatively young, with perhaps the work on TravisTorrent the
most cited and central one.
We also know there have been scattered
research efforts on build log analysis, mostly where the
log analysis was a side-part of the article.
To the best of our
knowledge, there has not been an attempt to systematically overview
and survey approaches for processing build logs,
despite their forseeable future and current importance.

\subsection{Study Selection}
% TODO shorten
\Cref{fig:lit-survey} presents an overview of our study selection.
In this first literature overview study on analyzing build logs, we
therefore want to survey as broad a population of scientific material
as possible.
Note that we do not limit our sources to specific
Software Engineering venues, as is often
done~\cite{petersen2015guidelines}, but survey all sources
monitored by Google Scholar, including Bachelor's and Master's theses,
academic slide decks, and books.
We use Google Scholar as opposed to
Scopus or other databases, as it is the search engine for acdemic
articles with the broadest and most current index, including preprints
from sources such as arXiv.
% TODO: maybe remove, this screams snowballing needed
One challenge is that no common
nomenclature has been established yet (in fact, this is one of the
goals of this article).

@@

First, we filtered out articles based on (1) their title and (2) the
contextual information Google Scholar displayed.
We inlcuded only
publications written in a language intelligible to the authors (that
is, English or German), which disregarded fewer than 1\% of search
hits.
Our strategy was to err on the side of
caution, that is rather including a paper than not.
We then unified
the results of the four search queries based on the link as the
identifying element, removing 60 articles that appeared in more than
one search query.
We removed further duplicates based on the title and were
left with 256 (16\%) of the original search results.
% removed duplicates of data extraction pass already here

With these 256 remaining articles, we followed a backward snowball
sampling for related work.
This added five papers (eight before
duplicate elimination) to our literature set, coming to a total of 261
articles.

On the surviving artciles, we did a second filter phase by downloading the
full articles, reading their abstracts, and searching the full text
for the occurrence of ``log''.
If these papers showed traces of
working with build logs, we included them in our survey.
In total, we
were left with 87 articles after this search.

\subsection{Article Classification}
Having trimmed down the set of articles, we investigated them in depth.
We kept all articles that use logs from software builds as input to
some kind of process and excluded another 15 articles.
For several cases, multiple articles extended others, though still
reported on
the same work with the respect to processing build logs.
Of these we only considered the earliest article which reported on
the processing of build logs.
This excluded 11 articles from our survey.
In sum, we further classify 61 articles.

@@

\begin{figure*}
\centering
    \textbf{PBE, CTS, KWS, and RLR}\par\medskip
\begin{subfigure}[b]{\columnwidth}
		\centering
				\includegraphics[width=\columnwidth,
				clip]{img/big-study/recall-precision-singlecategory-all.pdf}
		\caption{Training and test examples are in \emph{one}
		structural category.\\ \,}
    % top-aligning captions
		\label{fig:recall-precision-singlecategory-all}
\end{subfigure}\hspace{\fill}
\begin{subfigure}[b]{\columnwidth}
		\centering
				\centering
		\includegraphics[width=\columnwidth,
		clip]{img/big-study/recall-precision-multicategory-all.pdf}
		\caption{Training and test examples are in $>1$ structural
		category.}
		\label{fig:recall-precision-multicategory-all}
\end{subfigure}
\caption{Precision, recall and F$_{1}$-score of all
techniques compared, split by structural category count.}
\end{figure*}

>>>>

% TODO (Caro): Integrate Petersen's guidelines
The field of analyzing build
logs is relatively young; we know there have been scattered
research efforts on build log analysis, mostly where the
log analysis was a side-part of the article.
To the best of our
knowledge, there has not been an attempt to systematically overview
and survey approaches for processing build logs.

\subsection{Study Selection}
% TODO shorten
\Cref{fig:lit-survey} presents an overview of our study selection.
In this first literature overview study on analyzing build logs, we
 survey as broad a population of scientific material as possible. We
 do not limit our sources to specific Software Engineering venues, as
 is often done~\cite{petersen2015guidelines}, but survey all sources
 monitored by Google Scholar, including Bachelor's and Master's
 theses, academic slide decks, and books, since the field of build log
 analysis is so young.  We use Google Scholar as opposed to Scopus or
 other databases, as it is the search engine for acdemic articles with
 the broadest and most current index, including preprints from sources
 such as arXiv.
% TODO: maybe remove, this screams snowballing needed
One challenge is that no common
nomenclature has been established yet (in fact, this is one of the
goals of this article).

@@

First, we filtered articles based on (1) their title and (2) the
contextual information Google Scholar displayed.
We inlcuded only
publications written in a language intelligible to the authors (that
is, English or German), which disregarded fewer than 1\% of search
hits.
Our strategy for this round was to err on the side of
caution, that is rather including a paper than not.
We then unified
the results of the four search queries based on the link as the
identifying element, removing 60 articles that appeared in more than
one search query.
We removed further duplicates based on the title and were
left with 256 (16\%) of the original search results.
% removed duplicates of data extraction pass already here

With these 256 remaining articles, we followed a backward snowball
sampling for related work. This meant that we added an article if referred in them in the context of log analysis. 
This added five papers (eight before
duplicate elimination) to our literature set, coming to a total of 261
articles.

Subsequently, we did a second, finer filter phase by downloading the
full articles, reading their abstracts, and searching the full text
for the occurrence of ``log''.
If these papers showed traces of
working with build logs, we included them in our survey.
In total, we
were left with 87 articles after this search.

\subsection{Article Classification}
Having trimmed down the set of articles, we investigated them in depth.
We kept all articles that use logs from software builds as input to
some kind of process and excluded another 15 articles.
For several cases, multiple articles were extensions of others.
Of these we only considered the earliest article which reported on
the processing of build logs.
This excluded 11 articles from our survey.
In sum, we further classified 61 articles.

@@

\begin{figure*}
\centering
    \textbf{PBE, CTS, KWS, and RLR}\par\medskip
\begin{subfigure}[b]{\columnwidth}
		\centering
				\includegraphics[width=\columnwidth,
				clip]{img/big-study/recall-precision-singlecategory-all.pdf}
		\caption{Training and test examples in \emph{one}
		structural category.\\ \,}
    % top-aligning captions
		\label{fig:recall-precision-singlecategory-all}
\end{subfigure}\hspace{\fill}
\begin{subfigure}[b]{\columnwidth}
		\centering
				\centering
		\includegraphics[width=\columnwidth,
		clip]{img/big-study/recall-precision-multicategory-all.pdf}
		\caption{Training and test examples in $>1$ structural
		category.}
		\label{fig:recall-precision-multicategory-all}
\end{subfigure}
\caption{Precision, recall and F$_{1}$-score of all
techniques compared, split by structural category count.}
\end{figure*}
